Double White Dwarf Mergers on Adaptive Meshes\\ I. Methodology and Code Verification

### 2015-08-10 papers/wdmerger_I/paper.tex
Add gravitational wave verification to paper.

>>>>

As a simple verification test to ensure our gravitational wave calculations are correct, we plot the 
gravitational wave strain along the rotation axis for the first two periods of the unequal mass system. 
At this early time the orbit is circular and so to a good approximation we expect that the gravitational 
wave signal should be that of two point masses, whose positions are:
\begin{align}
  \mathbf{r}_P(t) &= -a_P\, \text{cos}(\omega t) \hat{x} - a_P\, \text{sin}(\omega t) \hat{y} \\
  \mathbf{r}_S(t) &= a_S\, \text{cos}(\omega t) \hat{x} + a_S\, \text{sin}(\omega t) \hat{y}.
\end{align}
Then the mass distribution is $\rho(\mathbf{r}) = M_P\, \delta^3(\mathbf{r} - \mathbf{r}_P) + M_S\, \delta^3(\mathbf{r} - \mathbf{r}_S)$.
From this it is straightforward to calculate the quadruopole tensor, take its second time derivative, and then apply the 
projection operator to get the gravitational wave polarizations along the rotation axis:
\begin{align}
  h_+ &= -4\frac{G\mu}{c^4 r}\left[G M_{\text{tot}} \omega \right]^{2/3}\, \text{cos}(2\omega t) \\
  h_\times &= -4\frac{G\mu}{c^4 r}\left[G M_{\text{tot}} \omega \right]^{2/3}\, \text{sin}(2\omega t).
\end{align}
$\mu$ is the reduced mass, while $M_{\text{tot}}$ is the total mass. From this we see that the 
gravitational wave frequency is twice the orbital frequency, and that the two polarizations 
are out of phase by $90^\circ$ in time. We compare this analytical expectation to the 
numerical results in \autoref{fig:gw_strain}. We find very good agreement in this case, and this 
level of agreement holds in the rotating frame as well.

\begin{figure}
  \centering
  \includegraphics[scale=0.45]{plots/unequal_gw_rot0.eps}
  \caption{Gravitational wave strain polarizations for the first two orbital periods of the 
           unequal mass system. The curves with markers are the numerical data, while the 
           curves without markers are the analytical results for two point masses.\label{fig:gw_strain}}
\end{figure}
